% Chapter 1

\chapter{Introduction} % Write in your own chapter title
\label{Chapter1}
\lhead{Chapter 1. \emph{Introduction}} % Write in your own chapter title to set the page header

{
This is a desktop based WindowsFormsApp(.NET Framework) application which is using Microsoft SQL database for the data storage and manipulation. In this system the procedure of managing final term project has been automated. As MS SQL server is being used in this system for data storage and manipulation, so, data will be more secured and user don't need to worry about the loss of data or it's piracy.
The basic working algorithm of data is based on a case study provided to us by Mr. Nazeef ul Haq (Lecturer Computer Science department UET Lahore). The main understanding was developed from same case study. The whole working procedure that was extracted from case study and it's implementation is discussed in below sections.
}
\section{Operational Details}
{
Department of Computer Science UET Lahore holds committee for management of final year project. Each year, 
list of project titles is opened for the students by the committee after the compilation of ideas from the faculty 
members. Students are privileged to form the group and select any of the ideas from the list after approval from 
the faculty advisor. Once the project is selected by a group of students, an advisory board is assigned to the project 
which consists of main advisor, co-advisor, and industry advisor. The member of project committee is supposed to manage data at one place. Which includes the management of :
\begin{itemize}
    \item Students  and Formation of Student Group and its management 
    \item Advisors  and Assignment of multiple advisors to the project 
    \item Projects 
    
    \item Evaluations
    
\end{itemize}
}
